### 2020-01-01 methods.tex
added methods section

We assume the model has been (or will be) trained on (unspecified) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, 
using Backprop, by minimizing the loss $\mathcal{L}$ 
For simplicity, we do not indicate the structural details of the layers (e.g., Dense or not, Convolutions or not, Residual/Skip Connections, etc.).

Each layer contains by one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or the 2D feature maps $\mathbf{W}_{i,L}$ 
extracted from 2D Convolutional layers.

>>>>

The model has been (or will be) trained on (unspecified) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, 
using Backprop, by minimizing the loss $\mathcal{L}()$.  (comment on regularization, dropout, etc).  Each layer contains by one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or the 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers.  (For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below.)

We assume the layer weight matrices are statistically independent, allowing us to estimate the Complexity, or test accuracy, with a standard Product Norm

\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\Vert\mathbf{W}\Vert$ may be the Frobenius norm, the Spectral Norm, or even p-Norm (Shatten Norm).

DEFINE EACH HERE

One can view $\mathcal{C}$ as something akin to a data dependent VC complexity.

CLARIFY HOW CONV2D lsyers are treated

\begin{eqnarray*}
\log\mathcal{C} &\sim& \log\bigg[\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert\bigg]  \\
                &\sim& \bigg[\log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert\cdots\log\Vert\mathbf{W}_{L}\Vert\bigg]  ,
\end{eqnarray*}
and we define the average log norm of the weight matrices as
